### 2018-08-06 article.tex

\begin{definition}  \label{def:strict-two-cat}
A \emph{strict} 2-category \catC is a category \emph{enriched over
  \textbf{Cat}}, the category of categories, \emph{viz:}
\begin{itemize}
\item A category \catC, whose objects and arrows are known as
  0-cells and 1-cells respectively.
\item For every pair of objects $A$ and $B$, we have a
  category $\catC(A, B)$, whose arrows are known as 2-cells.
\item For 2-cells $\alpha : f \Rightarrow g$ and $\beta : g
  \Rightarrow h$ in $\catC(A,B)$ their (vertical) composite is denoted
  $\beta\bullet\alpha : f \Rightarrow h$.
\item For every 1-cell $f:A\to B$ we denote its identity 2-cell by
  $Id_f:f \Rightarrow f$.
\item For all 0-cells $a$, $b$, $c$ a bifunctor $\circ: \catC(b, c)
  \times \catC(a, b) \to \catC(a, c)$ called \emph{horizontal
    composition} of 2-cells.
\end{itemize}
\REM{Need here the name for a 2-cat with all 2-cells invertible;  the
  term 2-groupoid refers to the case where both 1- and 2-cells are
  invertible.}
\end{definition}

@@

\begin{definition}\label{def:monoidal-two-cat}
A \emph{strict} monoidal 2-category $(\catC, \otimes)$ is a strict
2-category with
\REM{Is this \emph{required}?  Doesn't it follow from the  definition
  of bifunctor?  (It does in the 1-category case, so it should do
  here!)}
\begin{itemize}
\item a 2-bifunctor $\otimes: \catC \times \catC \to \catC$ such that
  on 2-cells $r, s, t, u$
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\REM{This definition doesn't quite work without the additoin type
  information on the 2-cells}
\end{itemize}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        INTERCHANGE LAW REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}[Interchange law]
Since $\circ$ and $\otimes$ are bifunctorial, we have the following
interchange equations for all 0-cells $A, B \in \catC$ and all 2-cells $r, s,
    t, u \in \catC(A, B)$
\begin{align}
(r \circ s) \bullet (t \circ u) &= (r \bullet t) \circ (s \bullet u) \\
(r \otimes s) \bullet (t \otimes u) &= (r \bullet t) \otimes (s \bullet u)
\end{align}
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
A \emph{groupoid} is a category where morphisms are invertible.
Let's define the following strict monoidal 2-groupoid \catC

\begin{itemize}
\item 0-cells are natural number $\mathbb{N}$
\item 1-cells are quantum circuits freely generated by $\circ$, $\otimes$ and
  $\{f_i\}_i$, a set of quantum circuits
\item 2-cells are quantum circuit transformations freely generated by $\circ$,
  $\otimes$ and $\{r_i\}_i$, a set of ransformations, such that $\forall r: f
    \Rightarrow g \in \{r_i\}_i, \exists r^{-1}: g \Rightarrow f \in \{r_i\}_i$
\[
r \circ r^{-1} = id_f
\]
\item the vertical composition is the usual transformations composition
\item the horizontal composition is the usual circuits composition
\item the 2-bifunctor is
\begin{itemize}
\item on 0-cell, $a \otimes b = a + b$
\item on $\catC(a, b)$, a functor $\catC(a, b) \otimes C(a', b') \to C(a + a',
  b + b')$
\end{itemize}
\end{itemize}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
For all transformation $r: f \Rightarrow g$, $r$ can be writen
\[
r = r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet r_i
\]

\begin{proof}
We'll prove it by induction of the size of the transformation using the
  properties of the bifunctors.
With a single transformation, we already have
\[
r = r_1
\]
For the inductive step let's assume $r$ is
\[
r = r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet s
\]
If $s$ is such that
\[
s = (s_1 \bullet s_2) \circ (s_3 \bullet s_4)
\]
Then using the interchange law we can write
\[
s = (s_1 \circ s_3) \bullet (s_2 \circ s_4)
\]
So we have 
\begin{align}
r &= r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet (s_1 \circ s_3) \bullet
  (s_2 \circ s_4) \cr
r &= r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet r_{i - 1} \bullet r_i
\end{align}
Otherwise we can always add an identity transformation to get the interchange
  law.
\begin{align}
s_1 \circ (s_3 \bullet s_4) &\Rightarrow (s_1 \bullet id) \circ (s_2 \bullet
  s_3) \cr
(s_1 \bullet s_2) \circ s_3 &\Rightarrow (s_1 \bullet s_2) \circ (id \bullet
  s_3)
\end{align}
The same is true with
\[
s = (s_1 \bullet s_2) \otimes (s_3 \bullet s_4)
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
For all transformation $r: f \Rightarrow g$, $r$ can be writen
\begin{align}
r &= r_1 \circ r_2 \circ r_3 \circ \cdots \circ r_j \cr
r &= r_1 \otimes r_2 \otimes r_3 \otimes \cdots \otimes r_k
\end{align}

\begin{proof}
The proof is the same but this time we have to use
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformation $r: f \Rightarrow g$, $r$ can be writen
\[
r = r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet r_i
\]
Such that for all $i$
\[
r_i = r_{i, 1} \circ r_{i, 2} \circ r_{i, 3} \circ \cdots \circ r_{i, j}
\]
and for all $j$
\[
r_{i, j} = \bigotimes_k^l r_{i, j, k}
\]
a tensor products of transformations.
\end{corollary}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[$\mathbb{Q}$-enriched category]
A $\mathbb{Q}$-enriched category \catE is

\begin{itemize}
\item A set of objects
\item For all objects $(a, b)$, $\catE(a, b) \in \mathbb{Q}$
\end{itemize}

such that for all object $a$
\[
e \succeq \catE(a, a)
\]
for all objects (a, b, c)
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Monoidal $\mathbb{Q}$-enriched category]
$(E, \otimes)$ is strictly monoidal if
\[
\catE(a, b) \oplus \catE(a', b') \succeq \catE(a \otimes a', b \otimes b')
\]
and symmetric if
\[
e \succeq \catE(a \otimes b, b \otimes a)
\]
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[$\catC(a, b)$ to $\mathbb{Q}$ homomorphism]
Let's define the following homomorphism $F$ from $\catC(a, b)$ to $\mathbb{Q}$.
  For all $f: a \to b \in \{f_i\}_i$
\[
V(f) \in \mathbb{Q}
\]
For all $r: f \Rightarrow g \in \{r_i\}_i$
\[
V(r) = V(f) \oplus V(g)^{-1}
\]

On 1-cells
\begin{align}
V(f \circ g) &\preceq V(f) \oplus V(g) \cr
V(f \otimes g) &\preceq V(f) \oplus V(g)
\end{align}

On 2-cells
\begin{align}
V(r \circ s) &= V(r) \oplus V(s) \cr
V(r \otimes s) &= V(r) \oplus V(s) \cr
V(r \bullet s) &= V(r) \oplus V(s)
\end{align}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
Note that because
\[
V(r: f \Rightarrow g) = V(f) \oplus V(g)^{-1}
\]
then
\begin{align}
V(r: f \Rightarrow f) &= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
that is
\begin{align}
\forall f, V(id_f) = e
\end{align}
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
Given two transformations $r, s: f \Rightarrow g$, then $V(r) = V(s)$.

\begin{proof}
The set of all possible transformation is freely generated by $\{r_i\}_i$,
  $\bullet$, $\circ$ and $\otimes$ so both $r$ and $s$ can be written
\begin{align}
r &= r_1 \odot r_2 \odot r_3 \odot \cdots \odot r_n \cr
s &= s_1 \odot s_2 \odot s_3 \odot \cdots \odot s_m
\end{align}
with $\odot \in \{\bullet, \circ, \otimes\}$ and for all i
\begin{align}
r_i &\in \{f_i\}_i \cr
s_i &\in \{f_i\}_i
\end{align}
If $n = 1$ then $r \in \{f_i\}_i$, so $V(r) = V(f) \oplus V(g)^{-1}$.
Otherwise
\begin{align}
V(r) &= V(r_1 \odot r_2 \odot \cdots \odot r_n) \cr
&= V(r_1) \oplus V(r_2) \oplus \cdots \oplus V(r_n) \cr
&= V(f \Rightarrow h_1) \oplus V(h_1 \Rightarrow h_2) \oplus \cdots \oplus
  V(h_n \Rightarrow g) \cr
&= V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus \cdots
  \oplus V(h_n) \oplus V(g)^{-1}
\end{align}
A easy inductive proof can show us that
\[
V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus V(h_2) \oplus
  \cdots \oplus V(h_n) \oplus V(g)^{-1} = V(f) \oplus V(g)^{-1}
\]
The same is true for $s$, so
\[
V(r) = V(s) = V(f) \oplus V(g)^{-1}
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformations $r: f \Rightarrow g$, then $V(r) = V(f) \oplus
  V(g)^{-1}$.
Note that the definition of $F$ gives that only for $r \in \{f_i\}_i$.
\end{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
The following category $\catC(\mathbb{Q})$ is a $\mathbb{Q}$-category
\begin{itemize}
\item A set of objects which are the 1-cells of $\catC$
\item For all objects $(f, g)$
\end{itemize}
\[
\catE(f, g) = \begin{cases} {\rm if~} f \Rightarrow g \in \catC, &V(f
  \Rightarrow g) \cr {\rm otherwise~} &\top \end{cases}
\]
With $\top \in Q$ such that for all $x \in \mathbb{Q}$
\[
x \preceq \top
\]

\begin{proof}
For all 1-cells $(f, g)$, if it exists a unique transformation $f \Rightarrow
  g$, then
\begin{align}
\catE(f, g) &= V(f \Rightarrow g) \in \mathbb{Q} \cr
&= V(f) \oplus V(g)^{-1}
\end{align}
otherwise we already have $\catE(f, g) = \top \in \mathbb{Q}$.
For all 1-cell $f$, we know that there is a identity transformation $f
  \Rightarrow f$ and
\begin{align}
\catE(f, f) &= V(id_f) \cr
&= V(f \Rightarrow f)\cr
&= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
Finally, for all 1-cells $(f, g, h)$ such that there exists $r: f \Rightarrow
  g$ and $s: g \Rightarrow h$ in $\catC$, then the homomorphism $F$ give us
\begin{align}
\catE(f, h) &= V(f \Rightarrow h) \cr
&= V(s\circ r) \cr
&= V(s) \oplus V(r) \cr
&= V(g \Rightarrow h) \oplus V(f \Rightarrow g) \cr
&= \catE(g, h) \oplus \catE(f, g)
\end{align}
If either $r$ or $s$ doesn't exists in $\catC$ then
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
become
\[\begin{matrix}
&\catE(b, c) \oplus \top &\succeq \top \cr
{\rm or~} &\top \oplus \catE(a, b) &\succeq \top \cr
{\rm or~} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 3        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
$\catC(\mathbb{Q})$ is strictly symmetric monoidal with $\otimes$, the
  2-functor of $\catC$.

\begin{proof}
The monoidal structure is immediate using the fact that
\[
V(r) \oplus V(s) \succeq V(r \otimes s)
\]
that is
\[
V(r: f \Rightarrow g) \oplus V(s: f' \Rightarrow g') = V(r \otimes s: f \otimes
  f' \Rightarrow g \otimes g')
\]
so
\[
\catE(f, g) \oplus \catE(f', g') = \catE(f \otimes f', g \otimes g')
\]
For the symmetry, we use the fact that $V(f \Rightarrow g) \oplus V(g
  \Rightarrow f) = e$
\begin{align}
\catE(f \otimes g, g \otimes f) &= V(f \otimes g \Rightarrow g \otimes g) \cr
&= V(f \Rightarrow g \otimes g \Rightarrow f) \cr
&\preceq V(f \Rightarrow g) \oplus V(g \Rightarrow f) \cr
&= V(f) \oplus V(g)^{-1} \oplus V(g) \oplus V(f)^{-1} \cr
&= e
\end{align}
\end{proof}
\end{proposition}

>>>>

\begin{definition}  \label{def:strict-two-cat}
A \emph{strict} 2-category $\mathcal{C}$ is a category \emph{enriched over
  \textbf{Cat}}, the category of categories, \emph{viz:}
\begin{itemize}
\item A category $\mathcal{C}$, whose objects and arrows are known as
  0-cells and 1-cells respectively.
\item For every pair of objects $A$ and $B$, we have a
  category $\mathcal{C}(A, B)$, whose arrows are known as 2-cells.
\item For 2-cells $\alpha : f \Rightarrow g$ and $\beta : g
  \Rightarrow h$ in $\mathcal{C}(A,B)$ their (vertical) composite is denoted
  $\beta\bullet\alpha : f \Rightarrow h$.
\item For every 1-cell $f:A\to B$ we denote its identity 2-cell by
  $Id_f:f \Rightarrow f$.
\item For all 0-cells $a$, $b$, $c$ a bifunctor $\circ: \mathcal{C}(b, c)
  \times \mathcal{C}(a, b) \to \mathcal{C}(a, c)$ called \emph{horizontal
    composition} of 2-cells.
\end{itemize}
\REM{Need here the name for a 2-cat with all 2-cells invertible;  the
  term 2-groupoid refers to the case where both 1- and 2-cells are
  invertible.}
\end{definition}

@@

\begin{definition}\label{def:monoidal-two-cat}
A \emph{strict} monoidal 2-category $(\mathcal{C}, \otimes)$ is a strict
2-category with
\REM{Is this \emph{required}?  Doesn't it follow from the  definition
  of bifunctor?  (It does in the 1-category case, so it should do
  here!)}
\begin{itemize}
\item a 2-bifunctor $\otimes: \mathcal{C} \times \mathcal{C} \to \mathcal{C}$
  such that on 2-cells $\alpha, \beta, \gamma, \delta$
\[
(\alpha \otimes \beta) \circ (\gamma \otimes \delta) = (\alpha \circ \gamma)
  \otimes (\beta \circ \delta)
\]
\REM{This definition doesn't quite work without the additoin type
  information on the 2-cells}
\end{itemize}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        INTERCHANGE LAW REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}[Interchange law]
Since $\circ$ and $\otimes$ are bifunctorial, we have the following
interchange equations for all 0-cells $A, B \in \mathcal{C}$ and all 2-cells
  $\alpha, \beta, \gamma, \delta \in \mathcal{C}(A, B)$
\begin{align}
(\alpha \circ \beta) \bullet (\gamma \circ \delta) &= (\alpha \bullet \gamma)
  \circ (\beta \bullet \delta) \\
(\alpha \otimes \beta) \bullet (\gamma \otimes \delta) &= (\alpha \bullet
  \gamma) \otimes (\beta \bullet \delta)
\end{align}
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
Given a free PROP of quantum circuits, we can extend it to a 2-PROP
  $\mathcal{P}$ where
\begin{itemize}
\item gates form the set of 1-cells 
\item the 2-cells are generated by a finite set of \emph{rewriting} rules such
  that
\begin{itemize}
\item 2 rewriting rules with the same types must be equal
\item each rewriting rule must be invertible, that is $\mathcal{C}(A, B)$ is a
  \emph{groupoid} for all 0-cells $A, B$
\end{itemize}
\end{itemize}

2-cells are in general called \emph{rewrite sequence}, but if a rewrite sequence
  has only 1 occurence of a rewrite rule, it is called an \emph{atomic rule}.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM EXAMPLE        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{example}
TODO rewrite sequence \& atomic rule
\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
For all rewriting sequences $\alpha: f \Rightarrow g$, $\alpha$ can be writen
\[
\alpha = \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet
  \alpha_i
\]

\begin{proof}
We'll prove it by induction of the size of the rewriting sequence using the
  properties of the bifunctors.
With a atomic rule, we already have
\[
\alpha = \alpha_1
\]
For the inductive step let's assume $\beta$ is
\[
\alpha = \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet \beta
\]
If $s$ is such that
\[
\beta = (\beta_1 \bullet \beta_2) \circ (\beta_3 \bullet \beta_4)
\]
Then using the interchange law we can write
\[
\beta = (\beta_1 \circ \beta_3) \bullet (\beta_2 \circ \beta_4)
\]
So we have 
\begin{align}
\alpha &= \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet
  (\beta_1 \circ \beta_3) \bullet (\beta_2 \circ \beta_4) \cr
\alpha &= \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet
  \alpha_{i - 1} \bullet \alpha_i
\end{align}
Otherwise we can always add an identity rewriting rule to get the interchange
  law.
\begin{align}
\beta_1 \circ (\beta_3 \bullet \beta_4) &\Rightarrow (\beta_1 \bullet id) \circ
  (\beta_2 \bullet \beta_3) \cr
(\beta_1 \bullet \beta_2) \circ \beta_3 &\Rightarrow (\beta_1 \bullet \beta_2)
  \circ (id \bullet \beta_3)
\end{align}
The same is true with
\[
\beta = (\beta_1 \bullet \beta_2) \otimes (\beta_3 \bullet \beta_4)
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
For all rewriting sequences $\alpha: f \Rightarrow g$, $\alpha$ can be writen
\begin{align}
\alpha &= \alpha_1 \circ \alpha_2 \circ \alpha_3 \circ \cdots \circ \alpha_j \cr
\alpha &= \alpha_1 \otimes \alpha_2 \otimes \alpha_3 \otimes \cdots \otimes
  \alpha_k
\end{align}

\begin{proof}
The proof is the same but this time we have to use
\[
(\alpha \otimes \beta) \circ (\gamma \otimes \delta) = (\alpha \circ \gamma)
  \otimes (\beta \circ \delta)
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all rewriting sequences $r: f \Rightarrow g$, $r$ can be writen
\[
\alpha = \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet
  \alpha_i
\]
Such that for all $i$
\[
\alpha_i = \alpha_{i, 1} \circ \alpha_{i, 2} \circ \alpha_{i, 3} \circ \cdots
  \circ \alpha_{i, j}
\]
and for all $j$
\[
\alpha_{i, j} = \bigotimes_k^l \alpha_{i, j, k}
\]
a tensor products of rewriting sequences.
\end{corollary}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[$\mathbb{Q}$-enriched category]
A $\mathbb{Q}$-enriched category $\mathcal{E}$ is

\begin{itemize}
\item A set of objects
\item For all objects $(a, b)$, $\mathcal{E}(a, b) \in \mathbb{Q}$
\end{itemize}

such that for all objects $a$
\[
e \succeq \mathcal{E}(a, a)
\]
for all objects (a, b, c)
\[
\mathcal{E}(b, c) \oplus \mathcal{E}(a, b) \succeq \mathcal{E}(a, c)
\]
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Monoidal $\mathbb{Q}$-enriched category]
$(E, \otimes)$ is strictly monoidal if
\[
\mathcal{E}(a, b) \oplus \mathcal{E}(a', b') \succeq \mathcal{E}(a \otimes a',
  b \otimes b')
\]
and symmetric if
\[
e \succeq \mathcal{E}(a \otimes b, b \otimes a)
\]
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
For all $(A, B) \in \mathcal{P}$ we define a homomorphism $V: \mathcal{C}(A, B)
  \to \mathbb{Q}$, such that for all gates $f$
\[
V(f) \in \mathbb{Q}
\]
For all rewriting rules $\alpha: f \Rightarrow g$
\[
V(\alpha) = V(f) \oplus V(g)^{-1}
\]

On gates
\begin{align}
V(f \circ g) &\preceq V(f) \oplus V(g) \cr
V(f \otimes g) &\preceq V(f) \oplus V(g)
\end{align}

On rewriting sequences
\begin{align}
V(\alpha \circ \beta) &= V(\alpha) \oplus V(\beta) \cr
V(\alpha \otimes \beta) &= V(\alpha) \oplus V(\beta) \cr
V(\alpha \bullet \beta) &= V(\alpha) \oplus V(\beta)
\end{align}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
Note that because
\[
V(\alpha: f \Rightarrow g) = V(f) \oplus V(g)^{-1}
\]
then
\begin{align}
V(\alpha: f \Rightarrow f) &= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
that is
\begin{align}
\forall f, V(id_f) = e
\end{align}
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
Given two rewriting sequence $\alpha, \beta: f \Rightarrow g$, then $V(\alpha) =
  V(\beta)$.

\begin{proof}
The set of all possible rewriting sequences is freely generated by the set of
rewriting rules, $\bullet$, $\circ$ and $\otimes$ so both $\alpha$ and $\beta$
  can be written
\begin{align}
\alpha &= \alpha_1 \odot \alpha_2 \odot \alpha_3 \odot \cdots \odot \alpha_n \cr
\beta &= \beta_1 \odot \beta_2 \odot \beta_3 \odot \cdots \odot \beta_m
\end{align}
with $\odot \in \{\bullet, \circ, \otimes\}$ and for all i $\alpha_i$ and
$\beta_i$ are rewriting rule.
If $n = 1$ then $\alpha$ is a rewriting rule, so $V(r) = V(f) \oplus V(g)^{-1}$.
Otherwise
\begin{align}
V(\alpha) &= V(\alpha_1 \odot \alpha_2 \odot \cdots \odot \alpha_n) \cr
&= V(\alpha_1) \oplus V(\alpha_2) \oplus \cdots \oplus V(\alpha_n) \cr
&= V(f \Rightarrow h_1) \oplus V(h_1 \Rightarrow h_2) \oplus \cdots \oplus
  V(h_n \Rightarrow g) \cr
&= V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus \cdots
  \oplus V(h_n) \oplus V(g)^{-1}
\end{align}
A easy inductive proof can show us that
\[
V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus V(h_2) \oplus
  \cdots \oplus V(h_n) \oplus V(g)^{-1} = V(f) \oplus V(g)^{-1}
\]
The same is true for $\beta$, so
\[
V(\alpha) = V(\beta) = V(f) \oplus V(g)^{-1}
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all rewriting sequences $\alpha: f \Rightarrow g$, then $V(\alpha) = V(f)
  \oplus V(g)^{-1}$.
Note that the definition of $V$ gives that only for rewriting rules.
\end{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
The following category $\mathcal{P}(\mathbb{Q})$ is a $\mathbb{Q}$-category
\begin{itemize}
\item A set of objects which are the gates of $\mathcal{P}$
\item For all objects $(f, g)$
\end{itemize}
\[
\mathcal{E}(f, g) =
\begin{cases}
\textrm{if } f \Rightarrow g \in \mathcal{P}, &V(f \Rightarrow g) \cr
\textrm{otherwise } &\top
\end{cases}
\]
With $\top \in \mathbb{Q}$ such that for all $x \in \mathbb{Q}$
\[
x \preceq \top
\]

\begin{proof}
For all gates $(f, g)$, if it exists a unique transformation $f \Rightarrow
  g$, then
\begin{align}
\mathcal{E}(f, g) &= V(f \Rightarrow g) \in \mathbb{Q} \cr
&= V(f) \oplus V(g)^{-1}
\end{align}
otherwise we already have $\mathcal{E}(f, g) = \top \in \mathbb{Q}$.
For all gates $f$, we know that there is a identity transformation $f
  \Rightarrow f$ and
\begin{align}
\mathcal{E}(f, f) &= V(id_f) \cr
&= V(f \Rightarrow f)\cr
&= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
Finally, for all gates $(f, g, h)$ such that there exists $\alpha: f \Rightarrow
  g$ and $\beta: g \Rightarrow h$ in $\mathcal{P}$, then the homomorphism $V$
    give us
\begin{align}
\mathcal{E}(f, h) &= V(f \Rightarrow h) \cr
&= V(\alpha \circ \beta) \cr
&= V(\alpha) \oplus V(\beta) \cr
&= V(g \Rightarrow h) \oplus V(f \Rightarrow g) \cr
&= \mathcal{E}(g, h) \oplus \mathcal{E}(f, g)
\end{align}
If either $\alpha$ or $\beta$ doesn't exists in $\mathcal{P}$ then
\[
\mathcal{E}(b, c) \oplus \mathcal{E}(a, b) \succeq \mathcal{E}(a, c)
\]
become
\[\begin{matrix}
&\mathcal{E}(b, c) \oplus \top &\succeq \top \cr
\textrm{or} &\top \oplus \mathcal{E}(a, b) &\succeq \top \cr
\textrm{or} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 3        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
$\mathcal{P}(\mathbb{Q})$ is strictly symmetric monoidal with $\otimes$, the
  2-functor of $\mathcal{P}$.
